---
title: "Data Loading"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Data Loading}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `dv.loader` package simplifies the process of loading data files into R. It can read both `.rds` files (R's native data storage format) and `.sas7bdat` files (SAS data files) into memory. Note that the current version does not include functionality for direct database connections.

The package's primary function is `load_data_files()`, which provides flexible data loading capabilities. This versatile function can load multiple data files from any location on your system - the files can be scattered across different directories or stored together. Unlike the legacy `load_data()` function which requires all files to be in a single subdirectory, `load_data_files()` accepts arbitrary file paths, making it more powerful and flexible for data loading.

Below is an example of how to use `load_data_files()` to load multiple data files from different directories. 

```{r}
# Create a temporary directory for the example
temp_dir <- tempdir()

# Create subdirectories for ADAM and SDTM data
dir.create(file.path(temp_dir, "sub_dir1"))
dir.create(file.path(temp_dir, "sub_dir2"))

# Save example datasets from pharmaverse packages as RDS files
saveRDS(iris, file.path(temp_dir, "sub_dir1", "iris.rds"))
saveRDS(mtcars, file.path(temp_dir, "sub_dir2", "mtcars.rds"))

# Load both data files using load_data_files()
data_list <- dv.loader::load_data_files(
  file_paths = c(
    file.path(temp_dir, "sub_dir1", "iris.rds"),
    file.path(temp_dir, "sub_dir2", "mtcars.rds")
  )
)

# Display the structure of the loaded data
str(data_list)
```
